Argennon: A Scalable Cloud Based Smart Contract Platform

### 2022-08-13 tex/A.tex
Update abstract, fix typos and add draw.io diagram (#12)
* changed chapter 1 of whitepaper

* changed chapter 1 of whitepaper some more

* create folder for diagrams

* Added Argennon-fees.drawio

* remove empty file

* Update Argennon-fees.drawio

* typos, change PV-DB to PVC, and change confusing sentence

Co-authored-by: Behrouz <behrouz_ayati@yahoo.com>
Add more explanation about validators in intro
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

        The Argennon cloud is trustless and publicly verifiable. Computational Integrity (CI) is
        achieved by using succinct cryptographic proofs (STARK/SNARK)
        and data integrity is guaranteed by cryptographic accumulators. At the same time, a smart
        clustering algorithm keeps the bandwidth usage and the overhead of cryptography manageable
        for validators.

@@

    \end{abstract}
    \tableofcontents

>>>>

        The Argennon cloud is trustless and publicly verifiable. Computational Integrity (CI) is
        achieved by using succinct argument of knowledge systems (STARK/SNARK)
        and data integrity is guaranteed by cryptographic accumulators. At the same time, a smart
        clustering algorithm keeps the bandwidth usage and the overhead of cryptography manageable
        for validators.

@@

        These properties make it possible for Argennon to achieve very high transaction throughput while requiring no trust
        in central parties.  
    \end{abstract}
    \tableofcontents

### 2022-08-13 tex/sections/intro.tex
Add more explanation about validators in intro
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

To overcome these difficulties, Argennon\footnote{The classical pronunciation should be used:\textipa{/Ar"gen.non/}}
uses a Hybrid Proof of Stake consensus protocol, which is
capable of combining the benefits of a centralized and a decentralized system. A small committee of
delegates is democratically elected by users via the Argennon Decentralized Autonomous Governance system
(ADAGs). This committee usually\footnote{The election term and the number of committee members can be changed by the
ADAGs.} is elected for a one-year term, has five members, and is responsible for minting new
blocks of the Argennon blockchain.
Each minted block is required to get approved by its corresponding validator committee. Validator committees are very
large sets of validators including at least three percent of the maximum possible stake of the system. A block is
approved if it takes approval votes from at least \(2/3\) of the total stake of its validator committee.

>>>>

To overcome these difficulties, Argennon\footnote{The classical pronunciation should be used:\textipa{/Ar"gen.non/}}
uses a Hybrid Proof of Stake consensus protocol, which is
capable of combining the benefits of a centralized and a decentralized system. A small committee of
delegates is democratically elected by users via the Argennon Decentralized Autonomous Governance system
(ADAGs). This committee usually\footnote{The election term and the number of committee members can be changed by the
ADAGs.} is elected for a one-year term, has five members, and is responsible for minting new
blocks of the Argennon blockchain.
Each minted block is required to get approved by its corresponding validator committee.
Validator committees are very
large sets of validators including at least three percent of the maximum possible stake of the system.
Every committee of validators has an index between $0$ and $m - 1$, and is resposible for validating block number $n$,
if $n$ modulo $m$ equals the committee index. A block is approved if it takes approval votes from at least $2/3$ of
the total stake of its validator committee.
